Value-Suppressing Uncertainty Maps

### 2017-03-29 paper/template.tex
Study check in

@@

\subsection{Methods}

@@

\subsubsection{Participants}
\subsection{Results}

\section{Discussion}
\subsection{Limitations and Future Work}
% When should you use these things?

>>>>

We performed a crowd-sourced experiment on Amazon's Mechanical Turk in order to evaluate the effectiveness of VSUMs for integrating uncertainty and value information in thematic maps.

@@

@@

\subsection{Methods}
\subsubsection{Hypotheses}

\subsection{Results}
\subsubsection{Participants}

We limited our population to Turkers from the United States, with a prior task approval rate of at least 90\%. As the experimental tasks required multi-hue color perception, we presented participants with a set of Ishihara plates as a pretest, and excluded participants who either misidentified the values in the plates, or who self-reported as having a color vision deficiency (CVD) in the post-test. Based on piloting, we paid participants \$X dollars an hour, for a target rate of \$8/hour.

Certain stimuli in the identification task had no uncertainty
\section{Discussion}
\subsection{Limitations and Future Work}
% When should you use these things?
